Boundary Labeling for annotated documents

### 2018-02-09 LaTeX/Paper.tex
Paper: Finished Re-Write of 2.2. Program: No changes.

The routing part of the algorithm, works through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed in a reachable position that is also above its leader's source. We will also use fixed ports located in the top left corner of each label. 
The routing area will be used to bridge the gap between the highest currently reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader. \change{We will call the combination of this connecting leader and the leader generated within the routing graph a \emph{Source-Port-Path} or \emph{SP-Path}.}%Kann man das so sagen?

The routing algorithm itself uses a depth-first-search algorithm, with the Graph $G$ and the set of sites $V_{ann} \subset V$ as input. The path within $G$ will be monotonically increasing. The Algorithm terminates either when reaching the right text border or if all possible paths failed to reach the text border. The SP-Path generated by the algorithm is split into two parts: The path within the graph $(P \subset V)$, which contains all vertices travelled through on the way to the text area's border, and the OPO-Leader that connects to the Label's port. If the routing for any given site failed, the SP-path only consists of a single vertex - the site. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

>>>>

The routing part of the algorithm works through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed in a reachable position that is also above its leader's source. It will use fixed ports located in the top left corner of each label. 
The routing area will be used to bridge the gap between the highest currently reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader. \change{We will call the combination of this connecting leader and the leader generated within the routing graph a \emph{Source-Port-Path} or \emph{SP-Path}.}%Kann man das so sagen?

\change{The routing algorithm itself uses a depth-first-search algorithm, with the Graph $G$ and the set of sites $V_{ann} \subset V$ as input. The Algorithm terminates either when reaching the right text border or if all possible paths failed to reach the text border, and the resulting SP-Path will be monotonically increasing. This path is split into two parts: The path within the graph $(P \subset V)$, leading from the source to the text area's border, and the OPO-Leader that connects the text area's border with the Label's port. The former is realized as a list of vertices $V_{Path} \subset V$ the leader travels through, whereas the latter is determined by the rightmost vertex of $V_{Path}$, the Port, and the location of the P-Segment. If the routing for any given site failed, the SP-path only consists of a single vertex - the site.} (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)
